Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-24 ATVA 2025/experiments.tex
update

\begin{table}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		NodeID & $\UB$ by SAS& Time cost & $\UB$ by GS  & Time cost \\
		\hline
		0 & -1.4684063 & 66.9 & -1.3804709 & 71.6 \\
		\hline
		2 & -4.5550154 & 54.8 & -4.5424599 & 84.9 \\
		\hline
		3 & -4.4795618 & 69.9 & -4.4459532 & 71.2 \\
		\hline
		4 & -3.4594076 & 88.8 & -3.4784499 & 113 \\
		\hline
		5 & -5.5981178 & 94.8 & -5.6955818 & 93.7 \\
		\hline
		6 & -3.0597499 & 63.3 & -2.9797569 & 68.5 \\
		\hline
		7 & -4.1742691 & 73.4 & -4.0842553 & 88.6 \\
		\hline
		8 & 0.63875415 & 56.7 & 0.72631579 & 46.5 \\
		\hline
		9 & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
		\hline
		Average & -3.1647624
		 & 70.3
		  & -3.129414017 & 78.6
		  \\
		\hline
		Variance & 
		 & 184
		  &  & 359
		   \\
		\hline
	\end{tabular}
	\vspace*{1ex}
	\caption{Time cost and accuracy by SAS and GS. Here, smaller $\UB$ means higher accuracy and negative means verified.}
	\label{SAS_GS_similarTO}
\end{table}

>>>>

%	\begin{tabular}{|c|c|c|c|c|}
%	\hline
%	NodeID & $\UB$ by SAS& Time cost & $\UB$ by GS  & Time cost \\
%	\hline
%	0 & -1.4684063 & 66.9 & -1.3804709 & 71.6 \\
%	\hline
%	2 & -4.5550154 & 54.8 & -4.5424599 & 84.9 \\
%	\hline
%	3 & -4.4795618 & 69.9 & -4.4459532 & 71.2 \\
%	\hline
%	4 & -3.4594076 & 88.8 & -3.4784499 & 113 \\
%	\hline
%	5 & -5.5981178 & 94.8 & -5.6955818 & 93.7 \\
%	\hline
%	6 & -3.0597499 & 63.3 & -2.9797569 & 68.5 \\
%	\hline
%	7 & -4.1742691 & 73.4 & -4.0842553 & 88.6 \\
%	\hline
%	8 & 0.63875415 & 56.7 & 0.72631579 & 46.5 \\
%	\hline
%	9 & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
%	\hline
%	Average & -3.1647624
%	& 70.3
%	& -3.129414017 & 78.6
%	\\
%	\hline
%	Variance & 
%	& 184
%	&  & 359
%	\\
%	\hline
%\end{tabular}

\begin{table}
\begin{tabular}{|c|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|}
	\hline
	Node & 0 &  2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 &Avg& Var \\
	\hline
	SAS & -1.47 & -4.56 & -4.48 & -3.46 & -5.6 & -3.06 & -4.17 & 0.639 & -2.33 &-3.16& \\
	\hline
	Time/s & 66.9 & 54.8 & 69.9 & 88.8 & 94.8 & 63.3 & 73.4 & 56.7 & 64.6 &70.3& 184\\
	\hline
	GS & -1.38 & -4.54 & -4.45 & -3.48 & -5.7 & -2.98 & -4.08 & 0.726 & -2.28 &-3.13&\\
	\hline
	Time/s & 71.6 & 84.9 & 71.2 & 113 & 93.7 & 68.5 & 88.6 & 46.5 & 69.4 &78.6&359\\
	\hline
\end{tabular}
	\vspace*{1ex}
	\caption{Time cost and accuracy by SAS and GS. Here, smaller $\UB$ means higher accuracy and negative means verified.}
	\label{SAS_GS_similarTO}
\end{table}
